---
title: "Lab 1"
author: "Haley Jeppson, Ashish Jain, Vinny Paris"
date: "January 19, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
library(tidyverse)
library(viridis)

```

## Question 1
The last word on page 21 is "May"


**VINNY's problems:**

While trying to compile H. Wickham's Advanced R book I run into the following issue:

"grep: Inconsolata.log: No such file or directory
mktextfm: mf-nowin -progname=mf \mode:=ljfour; mag:=1; nonstopmode; input Inconsolata' failed to make Inconsolata.tfm."

I am using a mac and I believe that the problem is a font does not naturally exist on my computer. Certain pieces of the book were created though (including the dedictaion and copyright section). I have downloaded the Inconsolata file but am stuck figuring out how to move it to the Font directory in my library. So my question is two fold: 1) Am I on the right track? 2) How do I move a file around on a mac? Thank you!

**Ashish's Problems and Solutions:**

I also faced the same problem while knitting the H. Wickham's Advanced R book. The book is using the "Inconsolata" font which is not a default font in mac. So in order to debug it, I googled it.

**"Whenever in trouble use GOOGLE"**

While searching through the internet we found the solution. First, we downloaded the Inconsolota font from [link](https://cooltext.com/Download-Font-Inconsolata). After that, we followed [these](http://superuser.com/questions/56787/how-to-install-and-find-fonts-for-mac-os-x) instructions and copied the font file into the following folders.

* /Library/Fonts/
* /Users/username/Library/Fonts

Thank you Haley and Vinny for your help!!


## Question 2

#### Retrieving the Data



```{r}


tmax <- function(stationid){
  station <- paste("ushcn.v2.5.5.20170118/", stationid, ".raw.tmax", sep="")
  temps <- read_fwf(station, 
                   col_positions=  fwf_positions(
                     start=c( 1,13, rep(16+9*0:11, each=4) + c(1,7,8,9)), 
                     end  =c(11,16, rep(16+9*0:11, each=4) + c(6,7,8,9))))
  
names(temps) <- c("Station", "Year", 
                 paste0(rep(c("Value","DMflag", "QCflag", "DSflag"), 12), 
                        rep(1:12, each=4)))

temps <- temps %>% 
  gather(key="Month", value="Temp_Max", starts_with("Value"))
temps$Month <- as.numeric(gsub("Value", "", temps$Month))
temps$Temp_Max <- replace(temps$Temp_Max, 
                          temps$Temp_Max == -9999, NA)
temps$Temp_Max <- temps$Temp_Max/100
temps$YearMonth <- temps$Year+temps$Month/12
temps
}

data <- tmax("USH00011084")

head(data)

```

#### Visualizing the Data


```{r pressure, echo=FALSE}

data %>% ggplot(aes(x = YearMonth, Temp_Max, colour= Temp_Max)) + 
  geom_point()  +
  scale_color_viridis(option="B")

data %>% ggplot(aes(x = Year, Temp_Max, colour=Temp_Max)) + 
  geom_point() + facet_wrap(~Month, nrow=2) +
  scale_color_viridis(option="B")


data %>% ggplot(aes(x = Month, Temp_Max, colour=Year)) + 
  geom_point() +geom_jitter(width = 0.34)+
  scale_color_viridis(option="B")
```


